Two Mode Networks and Relational Similarity

### 2023-08-30 analysis.qmd
New matrix reord plot plus lit

# Setup
```{r setup}
    knitr::opts_chunk$set(include = TRUE, 
                          echo = FALSE, 
                          warning = FALSE, 
                          message = FALSE)
    library(here)
    library(patchwork)
```

@@

# Analysis
```{r}
    source("Functions/TwoModeCA.R")
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 3, d.r = 12, d.c = 12)
    a <- tmCA.res$A.plot + theme(axis.text.x = element_text(angle = 0, 
                                                            size = 9,
                                                            vjust = -3))
    b <- tmCA.res$corr.plot
    c <- tmCA.res$sim.plot.r
    d <- tmCA.res$sim.plot.c + theme(axis.text.x = element_text(angle = 0))
    e <- tmCA.res$eigvec.plot.r
    f <- tmCA.res$eigvec.plot.c
    g <- tmCA.res$eigval.plot.r
    h <- tmCA.res$eigval.plot.c
    e <- e + inset_element(g, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    f <- f + inset_element(h, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    png(file = here("Plots", "main.png"), width=950, height=1200)
        (a | e | f) / (c | d) / b
    dev.off() 
```

```{r}
    source("Functions/TwoModeCA.R")
    res <- TwoModeCA(A)
```

>>>>

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(cowplot)
   library(here)
   library(patchwork)
   library(dplyr)
   library(ggbump)
   library(ggplot2)
   library(ggrepel)
   library(igraph)
   library(pals)
   source(here("Functions", "TwoModeCA.R"))
   source(here("Functions", "reflections.R"))
   source(here("Functions", "ref.long.dat.R"))
```

@@

# Analysis
```{r}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- CA(A, graph = FALSE)
   c <- round(a$CA.res$u[, 2], 3)
   d <- round(b$row$coord[, 1], 3)
   e <- data.frame(c, d)
   ggscatter(e, x = "c", y = "d", label = rownames(A), repel = TRUE)
```

```{r Reflections Bump Charts}
   evens <- function(x) subset(x, x %% 2 == 0)
   odds <- function(x) subset(x, x %% 2 != 0)
   a <- reflections(A, iter = 26)
   p.e.r <- a$p.r[, evens(1:20)]
   p.o.r <- a$p.r[, odds(1:20)]
   p.o.r <- p.o.r[, -1]
   b <- ref.long.dat(a = a$p.r, b = a$g.r, max.iter = 26)
   plot.dat <- b$person$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = person))
   # geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 0.8)
   p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = person), 
                                    size = 4, nudge_x = -3)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 22), 
                              aes(x = n.iter, label = person), 
                              size = 4, nudge_x = 0.5)

   # fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p1 <- p + scale_color_manual(values=as.vector(cols25(18)))

   plot.dat <- b$group$even
   p <- ggplot(data = filter(plot.dat, n.iter < 22),
               mapping = aes(x = n.iter, y = ref, color = group))
   #geoms
   p <- p + geom_bump(linewidth = 1, smooth = 8, alpha = 0.4)
   p <- p + geom_point(size = 4, alpha = 1)
   p <-    p <- p + geom_text(data = filter(plot.dat, n.iter == 24), 
                              aes(x = n.iter, label = group), 
                              size = 4, nudge_x = -2)
   p <-    p <- p + geom_text_repel(data = filter(plot.dat, n.iter == 2), 
                                    aes(x = n.iter, label = group), 
                                    size = 4, nudge_x = -1)
   #fixings
   p <- p + theme_minimal_grid(font_size = 14, line_size = 0)
   p <- p + scale_x_continuous(limits = c(-4, 30), breaks = evens(2:20))
   p <- p + labs(x = "Reflection")
   p <- p + scale_y_reverse()
   p <- p + theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank()
        )
   p2 <- p + scale_color_manual(values=as.vector(cols25(15)))
   png(file = here("Plots", "pg-reflections.jpg"), width=750, height=950)
   p1 / p2
   dev.off()
```

```{r Comparative scatters}
   library(Matrix)
   library(FactoMineR)
   AAt <- A %*% t(A)
   AtA <- t(A) %*% A
   bon.res.r <- svd(AAt)$u[, 1]
   bon.res.c <- svd(AtA)$u[, 1]
   names(bon.res.r) <- rownames(A)
   names(bon.res.c) <- colnames(A)
   van.res.r <- TwoModeCA(A)$eigvec.r[, 1]
   van.res.c <- TwoModeCA(A)$eigvec.c[, 1]
   ref.res.r <- scale(reflections(A, iter = 30)$p.r[, 26])
   ref.res.c <- scale(reflections(A, iter = 30)$p.c[, 26])
   ca.res.r <- CA(A, graph = FALSE)$row$coord[, 1]
   ca.res.c <- CA(A, graph = FALSE)$col$coord[, 1]
   dat.r <- data.frame(cbind(a = bon.res.r, b = van.res.r, 
                  c = as.vector(ref.res.r), d = ca.res.r))

```

```{r Main Plot}
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 3, d.r = 12, d.c = 12)
    a <- tmCA.res$A.plot + theme(axis.text.x = element_text(angle = 0, 
                                                            size = 9,
                                                            vjust = -3))
    b <- tmCA.res$corr.plot
    c <- tmCA.res$sim.plot.r
    d <- tmCA.res$sim.plot.c + theme(axis.text.x = element_text(angle = 0))
    e <- tmCA.res$eigvec.plot.r
    f <- tmCA.res$eigvec.plot.c
    g <- tmCA.res$eigval.plot.r
    h <- tmCA.res$eigval.plot.c
    e <- e + inset_element(g, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    f <- f + inset_element(h, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    png(file = here("Plots", "main.png"), width=950, height=1200)
        (a | e | f) / (c | d) / b
    dev.off() 
```
